modelStudio - perks and features

### 2020-05-08 inst/doc/ms-perks-features.Rmd
version 1.1.0

`modelStudio::modelStudio` computes various (instance and dataset level) model explanations and produces an interactive, customizable dashboard made with D3.js. It consists of multiple panels for plots with their short descriptions. Easily save and share the dashboard with others. Tools for model exploration unite with tools for EDA (Exploratory Data Analysis) to give a broad overview of the model behavior.

@@

```{r results="hide"}
train <- DALEX::HR
train$fired <- ifelse(train$status == "fired", 1, 0)
train$status <- NULL

@@

Prepare `HR_test` data and a `randomForest` model for the explainer:

```{r results="hide", eval = FALSE}
# fit a randomForest model
library("randomForest")
model <- randomForest(fired ~., data = train)

@@

`N` is a number of observations used for calculation of
[Partial Dependence](https://pbiecek.github.io/ema/partialDependenceProfiles.html)
and [Accumulated Dependence](https://pbiecek.github.io/ema/accumulatedLocalProfiles.html) Profiles.
`B` is a number of permutation rounds used for calculation of
[Shapley Values](https://pbiecek.github.io/ema/shapley.html) and
[Feature Importance](https://pbiecek.github.io/ema/featureImportance.html).
Decrease `N` and `B` parameters to lower the computation time or increase
them to get more accurate empirical results.

@@

# slower, more precise
modelStudio(explainer,
            N = 800, B = 25)
```

@@

## plot options

Customize some of `modelStudio` looks by overwriting default options returned
by the `modelStudioOptions()` function. Full list of options:
[documentation](http://modelstudio.drwhy.ai/reference/modelStudioOptions.html).

```{r eval = FALSE}
# set additional graphical parameters
new_options <- modelStudioOptions(
  show_subtitle = TRUE,
  bd_subtitle = "Hello World",
  line_size = 5,
  point_size = 9,
  line_color = "pink",
  point_color = "purple",
  bd_positive_color = "yellow",
  bd_negative_color = "orange"
)

@@

@@

@@

# fit a model
task <- makeRegrTask(id = "task", data = train, target = "fired")

learner <- makeLearner("regr.randomForest", par.vals = list(ntree = 300), predict.type = "response")

model <- train(learner, task)

@@

# make a studio for the model
modelStudio(explainer_mlr,
            B = 10)
```

>>>>

`modelStudio::modelStudio` computes various (instance and dataset level) model explanations and produces
an interactive, customisable dashboard. It consists of multiple panels for plots with their short descriptions.
Easily save and share the HTML dashboard with others. Tools for model exploration unite with tools for
EDA (Exploratory Data Analysis) to give a broad overview of the model behavior.

@@

```{r results="hide"}
train <- DALEX::HR
train$fired <- as.factor(ifelse(train$status == "fired", 1, 0))
train$status <- NULL

@@

Prepare `HR_test` data and a `ranger` model for the explainer:

```{r results="hide", eval = FALSE}
# fit a ranger model
library("ranger")
model <- ranger(fired ~., data = train, probability = TRUE)

@@

`N` is a number of observations used for calculation of
[Partial Dependence](https://pbiecek.github.io/ema/partialDependenceProfiles.html)
and [Accumulated Dependence](https://pbiecek.github.io/ema/accumulatedLocalProfiles.html) Profiles. 
`10*N` is a number of observations used for calculation of
[Feature Importance](https://pbiecek.github.io/ema/featureImportance.html).
`B` is a number of permutation rounds used for calculation of
[Shapley Values](https://pbiecek.github.io/ema/shapley.html) and
[Feature Importance](https://pbiecek.github.io/ema/featureImportance.html).
Decrease `N` and `B` parameters to lower the computation time or increase
them to get more accurate empirical results.

@@

# slower, more precise
modelStudio(explainer,
            N = 500, B = 15)
```

@@

## additional options

Customize some of `modelStudio` looks by overwriting default options returned
by the `ms_options()` function. Full list of options:
[documentation](http://modelstudio.drwhy.ai/reference/ms_options.html).

```{r eval = FALSE}
# set additional graphical parameters
new_options <- ms_options(
  show_subtitle = TRUE,
  bd_subtitle = "Hello World",
  line_size = 5,
  point_size = 9,
  line_color = "pink",
  point_color = "purple",
  bd_positive_color = "yellow",
  bd_negative_color = "orange"
)

@@

All visual options can be changed after the calculations using `ms_update_options()`.

```{r eval = FALSE}
old_ms <- modelStudio(explainer)
old_ms

# update the options
new_ms <- ms_update_options(old_ms,
                            time = 0,
                            facet_dim = c(1,2),
                            margin_left = 150)
new_ms
```

@@

## update observations

Use `ms_update_observations()` to add more observations with their local explanations to the `modelStudio`.

```{r eval = FALSE}
old_ms <- modelStudio(explainer)
old_ms

# add new observations
plus_ms <- ms_update_observations(old_ms,
                                  explainer,
                                  new_observation = test[101:102,])
plus_ms

# overwrite old observations
new_ms <- ms_update_observations(old_ms,
                                 explainer,
                                 new_observation = test[103:104,],
                                 overwrite = TRUE)
new_ms
```

@@

# fit a model
task <- makeClassifTask(id = "task", data = train, target = "fired")
learner <- makeLearner("classif.ranger", predict.type = "prob")
model <- train(learner, task)

@@

# make a studio for the model
modelStudio(explainer_mlr)
```
